\begin{rubric}{Professional Presentations}
\subrubric{Poster Presentations}
\text{\hangindent=0.5in Barnes, C. D., Bosson, J. K., Brown, R. P., Carvallo, M. R., \& \textbf{Lenes, J. G.} (January, 2013).  My country, my self: Honor, identity, and aggressive opposition to national threats.  \textit{Poster presented at the annual meeting of the Society for Personality and Social Psychology}, New Orleans, LA. \par}
\text{\hangindent=0.5in \textbf{Lenes, J. G.}, \& Bosson, J. K. (January, 2013). Precarious manhood and men’s attributional biases in partner conflict. \textit{Poster presented at the annual meeting of the Society for Personality and Social Psychology}, New Orleans, LA.\par}
\text{\hangindent=0.5in Chen, J. I., Michniewicz, K. S., \textbf{Lenes, J. G.}, \& Bosson, J.K. (August, 2012). Stereotypes associated with masculine and feminine psychological disorders.  \textit{Poster presented at the annual meeting of the American Psychological Association}, Orlando, FL.\par}
\text{\hangindent=0.5in \textbf{Lenes, J. G.}, \& Bosson, J. K. (January, 2012). Gender threat and men's implicit evaluations of traditional and non-traditional women. \textit{Poster presented at the annual meeting of the Society for Personality and Social Psychology}, San Diego, CA. }

\subrubric{Symposium Presentaions}
\text{\hangindent=0.5in \textbf{Lenes, J. G.} (2013, November 9). Did he really drink the fish's blood?' Manhood as an Implicit Social Construct. \textit{Symposia accepted to the meeting of the Society of Southeastern Social Psychologists}, Augusta, GA.\par}
\text{\hangindent=0.5in \textbf{Lenes, J. G.} (2012, October 13). Manhood and the effects of gender salience on gendered coping mechanisms. \textit{Symposia conducted at the meeting of the Society of Southeastern Social Psychologists}, Gainesville, FL.}

\subrubric{Departmental Presentations}
\text{\hangindent=0.5in \textbf{Lenes, J. G.} (2013, November 1). ``Did he really drink the fish's blood?'' Manhood as an implicit social construct. \textit{Departmental Brown Bag Presentation}, Tampa, FL.\par}
\text{\hangindent=0.5in Annis, J., \textbf{Lenes, J. G.}, Westfall, H. A., \& Malmberg, K. J. (2013, September 27). A bayesian perspective on the list-length effect in recognition testing. \textit{Departmental Brown Bag Presentation}, Tampa, FL.\par}
\text{\hangindent=0.5in Michniewicz, K. M., Caswell, T. A., \textbf{Lenes, J. G.} \& Hettinger, V. E. (2013, September 28). Men and the struggle for manhood: Basic and applied research on precarious manhood and its implications across domains. \textit{Departmental Brown Bag Presentation}, Tampa, FL.\par}
\text{\hangindent=0.5in \textbf{Lenes, J. G.} (2012, April 6). Precarious manhood and men’s attributional biases in partner conflict. \textit{Departmental Brown Bag Presentation}, Tampa, FL.\par}

\end{rubric}
